Recent Advances in Underwater Basket Weaving Under the Extreme Pressure of the Mariana Trench

### 2025-03-06 template.qmd
done here

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[runningheads]{llncs}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[activate=false]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{2}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[misc]{ifsym}
\newcommand{\corr}{(\Letter)}
\makeatletter

\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Fig.}
\else
  \newcommand\figurename{Fig.}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter

\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Recent Advances in Underwater Basket Weaving Under the Extreme Pressure of the Mariana Trench},
  pdfauthor={André Lauren Benjamin; Calvin Cordozar Broadus Jr.; Antwan André Patton},
  pdfkeywords={First Keyword, Second Keyword, Another Keyword.},
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\hypersetup{nolinks=true}

\title{Recent Advances in Underwater Basket Weaving Under the Extreme
Pressure of the Mariana Trench}

\titlerunning{Underwater Basket Weaving Under Extreme Pressure}

\author{André Lauren Benjamin\inst{1} \and Calvin Cordozar Broadus
Jr.\inst{2,3} \corr \and Antwan André
Patton\inst{1}\orcidID{0000-1111-2222-3333}}

\authorrunning{A.L. Benjamin et al.}

\institute{Fictional Southern University, Savannah GA
31404, USA  \email{\{a.l.benjamin,a.a.patton\}@fsu.fake} \and Fictional
West Coast University, Long Beach CA
90840, USA  \email{ccb@fwcu.fake} \and Secondary European
Affiliation, Tiergartenstr.
17, 69121 Heidelberg, Germany  \email{lncs@springer.com}}

\begin{document}
\maketitle

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First Keyword \and Second Keyword \and Another Keyword.}

\end{abstract}

\section{Introduction}\label{sec-intro}

\subsection{Main Contributions}\label{main-contributions}

@@

\section{Related Work}\label{related-work}

\subsection{Basket Weaving}\label{basket-weaving}

\subsubsection{Underwater Basket
Weaving}\label{underwater-basket-weaving}

@@

\paragraph{Underwater Basket Weaving Under Difficult
Circumstances}\label{underwater-basket-weaving-under-difficult-circumstances}

The contribution should contain no more than four levels of headings.
Table~\ref{tbl-headings} gives a summary of all heading levels.

\begin{table}[t]

\caption{\label{tbl-headings}Table captions should be placed above the
tables.}

\centering{

\begin{tabular}{lll}
\toprule
Heading level &  Example & Font size and style\\
\midrule
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\bottomrule
\end{tabular}

}

\end{table}%

\section{Recent Advances from the Mariana
Trench}\label{recent-advances-from-the-mariana-trench}

@@

\begin{equation}\phantomsection\label{eq-linear}{
x + y = z
}\end{equation}

Please try to avoid rasterized images for line-art diagrams and schemas.
Whenever possible, use vector graphics instead (see
Fig.~\ref{fig-duck}).

\begin{figure}[t]

\centering{

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{example-image-duck.pdf}

}

\caption{\label{fig-duck}A figure caption is always placed below the
illustration. Please note that short captions are centered, while long
ones are justified by the macro package automatically.}

\end{figure}%

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}

\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}

For citations of references, we prefer the use of square brackets and
consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides a
sample reference list with entries for journal articles
\cite{ref_article1}, an LNCS chapter \cite{ref_lncs1}, a book
\cite{ref_book1}, proceedings without editors \cite{ref_proc1}, and a
homepage \cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\section{Experiments}\label{experiments}

\subsection{Experimental Setup}\label{experimental-setup}

\subsection{Experimental Results}\label{experimental-results}

\section{Discussion}\label{discussion}

\section{Conclusion}\label{conclusion}

@@

\bibliographystyle{splncs04}
\bibliography{bibliography}

\end{document}

>>>>

---
title: Recent Advances in Underwater Basket Weaving Under the Extreme Pressure of the Mariana Trench
title-running: Underwater Basket Weaving Under Extreme Pressure
format:
  quarto-ecml-pdf:
    keep-tex: true
  quarto-ecml-html: default
blind-review: false
author:
  - name: André Lauren Benjamin
    affiliations:
      - name: Fictional Southern University
        address: Savannah GA 31404
        country: USA
        url: \{a.l.benjamin,a.a.patton\}\@fsu.fake
        id: south
    url: https://example.org/
  - name: Calvin Cordozar Broadus Jr.
    corresponding: true 
    affiliations:
      - name: Fictional West Coast University
        address: Long Beach CA 90840
        country: USA
        url: ccb@fwcu.fake
      - name: Secondary European Affiliation
        address: Tiergartenstr. 17
        city: Heidelberg
        country: Germany
        postal-code: 69121 
        url: lncs@springer.com
  - name: Antwan André Patton
    orcid: '0000-1111-2222-3333'
    affiliations:
      - ref: south 
author-running: A.L. Benjamin et al.
abstract: |
  The abstract should briefly summarize the contents of the paper in 150--250 words.
keywords: [First Keyword, Second Keyword, Another Keyword.]
---

## Introduction {#sec-intro}

### Main Contributions

@@

## Related Work

### Basket Weaving

#### Underwater Basket Weaving

@@

##### Underwater Basket Weaving Under Difficult Circumstances

The contribution should contain no more than four levels of headings. @tbl-headings gives a summary of all heading levels.

::: {#tbl-headings tbl-pos='t'}
```{=latex}
\begin{tabular}{lll}
\toprule
Heading level &  Example & Font size and style\\
\midrule
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\bottomrule
\end{tabular}
```

Table captions should be placed above the tables.
:::

<!-- | Heading level | Example | Font size and style |
|------|------|------|
| Title (centered) | {\Large\bfseries Lecture Notes} | 14 point, bold |
| 1st-level heading | {\large\bfseries 1 Introduction} | 12 point, bold |
| 2nd-level heading | {\bfseries 2.1 Printing Area} | 10 point, bold |
| 3rd-level heading | {\bfseries Run-in Heading in Bold.} Text follows | 10 point, bold |
| 4th-level heading | {\itshape Lowest Level Heading.} Text follows | 10 point, italic |

: Table captions should be placed above the
tables. {#tbl-headings} -->

## Recent Advances from the Mariana Trench

@@

$$
x + y = z
$$ {#eq-linear}
Please try to avoid rasterized images for line-art diagrams and schemas. Whenever possible, use vector graphics instead (see
@fig-duck).

![A figure caption is always placed below the illustration. Please note that short captions are centered, while long ones are justified by the macro package automatically.](example-image-duck){#fig-duck width=100% fig-pos='t'}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
<!-- %
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
% -->
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}

<!-- Using Quarto theorem environments does not work, see here: https://github.com/pat-alt/quarto-ecml/issues/1 -->
<!-- ::: {#thm-sample}
This is a sample theorem. The run-in heading is set in bold, while the following text appears in italics. Definitions, lemmas, propositions, and corollaries are styled the same way.
:::

::: {.proof}
Proofs, examples, and remarks have the initial word in italics, while the following text appears in normal font.
::: -->

For citations of references, we prefer the use of square brackets and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides a sample reference list with entries for journal articles [@ref_article1], an LNCS chapter [@ref_lncs1], a book [@ref_book1], proceedings without editors [@ref_proc1], and a homepage [@ref_url1]. Multiple citations are grouped [@ref_article1;@ref_lncs1;@ref_book1], [@ref_article1;@ref_book1;@ref_proc1;@ref_url1].

## Experiments

### Experimental Setup

### Experimental Results

## Discussion

## Conclusion

@@
